---
title: "CSSS 503 Homework 1"
author: "Caz VanDevere"
date: "`r format(Sys.Date(), format='%B %d, %Y')`"
output:
  html_document:
    theme: readable
---

```{r, echo=FALSE}
library(pander)
```



# Introduction

This is a report about a dataset on Swiss socio-economic indicators of each of the 47 provinces in 1888, named 'swiss'.
```{r, echo=FALSE}
data(swiss)
```

First, let's make a Pander summary table:
```{r, echo=FALSE}
pander(summary(swiss), style = "rmarkdown", split.tables = 120)
#80 for regular width, 120 for wide slides
```



# Variable Investigation

Do we notice anything interesting in this data? It looks like the infant mortality rate is quite high. Let's dive into this more deeply.

```{r, echo=FALSE}
hist(swiss$Infant.Mortality,
    xlab = "Infant Mortality Rate", # X axis label
    main = "Infant Mortality Rate in the Provinces") # Title
```

The infant mortality rate appears to follow a normal distribution. with a mean at `r round(mean(swiss$Infant.Mortality),2)`.

Do other statistics follow similar distributional patterns? Let's look at the variable Catholic.

```{r, echo=FALSE}
hist(swiss$Catholic,
    xlab = "Percentage Catholic", # X axis label
    main = "Catholicism in the Provinces") # Title
```

We see that this variable has a distribution almost completely opposite of the previous variable. Let's investigate whether these variables correspond statistically.

# Ordinary Least Squares Bivariate Regression

To see if there is a statistical correlation between infant mortality rate and Catholic practice, we are going to run an ordinary least squares regression.
```{r, echo=FALSE}
testRTW=lm(as.numeric(swiss$Infant.Mortality)~swiss$Catholic,data=swiss)
summary(testRTW)
```

The p-value is above .05 and .10., so we can conclude the these two variables do not have a statistically significant correlation. 
  
  
  
  
  
  
  
  
  
  